%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {CSU: Natural User Interaction Lab} % Organization
    {Undergraduate Research Assistant} % Job title
    {Fort Collins, Colorado} % Location
    {May. 2020 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked directly with \textit{\href{https://compsci.colostate.edu/person/?id=22550A7530193FD205613DD09DD2EE6F&sq=t}{Dr. Francisco Ortega}} and \textit{\href{http://psywebserv.psych.colostate.edu/psylist/detail.asp?Num=15}{Dr. Benjamin Clegg}}, on projects bridging the Psychology and Computer Science departments.}
        \item {Designed experiments in Unity using C\# to write logic and collect data from participants in Virtual Reality environments.}
        \item {Created custom building simulator in VR from scratch using Unity and C\#.}
        \item {\underline{Utilized}:  C\#, unity,  Git,  GitHub,  Qualtrics, MRTK, Hololens 2, Oculus}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Independent} % Organization
    {iOS Developer} % Job title
    {Douglas County, Colorado} % Location
    {Jul. 2019 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, developed, and deployed \textit{\href{https://apps.apple.com/us/app/happy-car-app/id1567999750,}{Happy Car}} to the Apple app store.}
        \item {Developed an iOS  application using Swift for Douglas County Sheriffs Office.}
        \item {Designed a restful  back-end server using Python for secure storage of names and phone numbers.}
        \item {\underline{Utilized}:  Swift, SwiftUI,  Python, Flask, AWS Lambda, Cocoapods}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Valor Christian High School} % Organization
    {IT Intern} % Job title
    {Highlands Ranch, Colorado} % Location
    {Jul. 2016 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided hardware and software solutions for help desk tickets.}
        \item {Managed a JAMF environment of 550 Apple devices.}
        \item {Setup and management of 20 Aerohive network access points.}
        \item {\underline{Utilized}:  JAMF, Unix, Bash, macOS, Windows}
      \end{cvitems}
    }

% %---------------------------------------------------------
\end{cventries}
